Cross-relaxation in dense ensembles of NV centers and application to magnetometry

### 2022-12-04 Talks/Soutenance 2022/presentation.tex
aled

\begin{document}
\begin{frame}
\maketitle
\begin{center}
\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{logos}
\end{center}
\end{frame}

@@

\section{NV centers and diamonds in practice}
\subsection{Diamond properties}
\begin{frame}{Outline}
\tableofcontents[currentsection]
\end{frame}

@@

\subsection{Characterization}
\begin{frame}{Sensitivity of LFDM}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_sensi_LFDM}
\end{frame}

@@

\subsection{Applications}
\begin{frame}{Application: wide-field magnetometry}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_applications_wide_field_f-2}
\end{frame}

\subsection{Applications}
\begin{frame}{Application: wide-field magnetometry}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_applications_wide_field_f-1}
\end{frame}

\subsection{Applications}
\begin{frame}{Application: wide-field magnetometry}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_applications_wide_field_f}
\end{frame}

\section{Depolarization mechanisms in dense NV ensemble}
\subsection{Cross-relaxations}
\begin{frame}{Outline}
\tableofcontents[currentsection]
\end{frame}
\begin{frame}{Principle of cross-relaxation with NV centers}
\centering
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{Slide_CR_presentation}
\end{frame}

\begin{frame}{Example: Cross-relaxation between NV centers and VH$^-$}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_CR_VH}
\end{frame}

\begin{frame}{Cross-relaxation between NV centers and NV centers}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_CR_adamas}
\end{frame}

\subsection{The fluctuator model}
\begin{frame}{Presentation of the fluctuator model}
\centering
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{Slide_fluct_intro}
\end{frame}

\begin{frame}{Stretched exponential decay profile}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_T1_exp_stretch}
\end{frame}

\subsection{Low field depolarization mechanisms}
\begin{frame}{Zero field depolarization sources (theory)}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_0B_theorie}
\end{frame}

\begin{frame}{Angular sensitivity of LFDM}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_angular_sensitivity}
\end{frame}
\subsection{Conclusion}
\begin{frame}{Conclusion}

\begin{itemize}
\item The use of NV center ensemble for magnetometry is currently limited by the interactions between the spin defects.
\bigskip
\item Dipole-dipole interaction within dense ensemble of NV centers result in spin depolarization which is exacerbated at low magnetic field.
\bigskip
\item This depolarization can be used to perform microwave-free and orientation-free magnetometry at low magneitc field.
\bigskip
\item the LFDM sensitivity seem to be determined by the double-flips.
\end{itemize}

@@

\begin{frame}{Acknowledgments}

@@

\begin{frame}{NV center magnetometry sensitivity}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_NV_limite_sensi}
\end{frame}
\end{document}

@@

>>>>

%\beamertemplatenavigationsymbolsempty
%\setbeamerfont{page number in head/foot}{size=\large}
%\setbeamertemplate{footline}[frame number]

\expandafter\def\expandafter\insertshorttitle\expandafter{%
  \insertshorttitle\hfill%
  \insertframenumber\,}

\begin{document}
%\begin{frame}
%\maketitle
%\begin{center}
%\includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{logos}
%\end{center}
%\end{frame}

\begin{frame}
\centering
\begin{tcolorbox}[colback=blue!20!white]
\centering
\Large
Cross-relaxation in dense ensembles of NV centers and
application to magnetometry
\end{tcolorbox}
\bigskip
Clément Pellet-Mary PhD Defense
\bigskip
\includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{logos}
\end{frame}

@@

\section{NV center spin properties}
\subsection{Diamond properties}
\begin{frame}{Outline}
\tableofcontents[currentsection]
\end{frame}

@@

\subsection{Characterization}
\begin{frame}{Sensitivity of LFDM}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_sensi_LFDM-1}
\end{frame}

\begin{frame}{Sensitivity of LFDM}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_sensi_LFDM}
\end{frame}

@@

\begin{frame}{Application: wide-field magnetometry}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_applications_wide_field_f-2}
\end{frame}

\begin{frame}{Application: wide-field magnetometry}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_applications_wide_field_f-1}
\end{frame}

\begin{frame}{Application: wide-field magnetometry}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_applications_wide_field_f}
\end{frame}

\section{Depolarization mechanisms in dense NV ensemble}
\subsection{Cross-relaxations}
\begin{frame}{Outline}
\tableofcontents[currentsection]
\end{frame}

\begin{frame}{Principle of cross-relaxation with NV centers}
\centering
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{Slide_CR_presentation_f-5}
\end{frame}

\begin{frame}{Principle of cross-relaxation with NV centers}
\centering
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{Slide_CR_presentation_f-4}
\end{frame}

\begin{frame}{Principle of cross-relaxation with NV centers}
\centering
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{Slide_CR_presentation_f-3}
\end{frame}

\begin{frame}{Principle of cross-relaxation with NV centers}
\centering
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{Slide_CR_presentation_f-2}
\end{frame}

\begin{frame}{Principle of cross-relaxation with NV centers}
\centering
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{Slide_CR_presentation_f-1}
\end{frame}

\begin{frame}{Principle of cross-relaxation with NV centers}
\centering
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{Slide_CR_presentation_f}
\end{frame}

\begin{frame}{Example: Cross-relaxation between NV centers and VH$^-$}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_CR_VH_0}
\end{frame}

\begin{frame}{Example: Cross-relaxation between NV centers and VH$^-$}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_CR_VH_1}
\end{frame}

\begin{frame}{Example: Cross-relaxation between NV centers and VH$^-$}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_CR_VH_2}
\end{frame}

\begin{frame}{Example: Cross-relaxation between NV centers and VH$^-$}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_CR_VH_3}
\end{frame}

\begin{frame}{Example: Cross-relaxation between NV centers and VH$^-$}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_CR_VH_4}
\end{frame}

\begin{frame}{Cross-relaxation between NV centers and NV centers}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_CR_adamas_f-3}
\end{frame}

\begin{frame}{Cross-relaxation between NV centers and NV centers}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_CR_adamas_f-2}
\end{frame}

\begin{frame}{Cross-relaxation between NV centers and NV centers}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_CR_adamas_f-1}
\end{frame}

\begin{frame}{Cross-relaxation between NV centers and NV centers}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_CR_adamas_f}
\end{frame}

\subsection{The fluctuator model}
\begin{frame}{Presentation of the fluctuator model}
\centering
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{Slide_fluct_intro_f-4}
\end{frame}

\begin{frame}{Presentation of the fluctuator model}
\centering
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{Slide_fluct_intro_f-3}
\end{frame}

\begin{frame}{Presentation of the fluctuator model}
\centering
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{Slide_fluct_intro_f-2}
\end{frame}

\begin{frame}{Presentation of the fluctuator model}
\centering
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{Slide_fluct_intro_f-1}
\end{frame}

\begin{frame}{Presentation of the fluctuator model}
\centering
\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{Slide_fluct_intro_f}
\end{frame}

\begin{frame}{Stretched exponential decay profile}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_T1_exp_stretch_f-1}
\end{frame}

\begin{frame}{Stretched exponential decay profile}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_T1_exp_stretch_f}
\end{frame}

\subsection{Low field depolarization mechanisms}
\begin{frame}{Zero field depolarization mechanisms (theory)}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_0B_theorie_f-5}
\end{frame}

\begin{frame}{Zero field depolarization mechanisms (theory)}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_0B_theorie_f-4}
\end{frame}

\begin{frame}{Zero field depolarization mechanisms (theory)}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_0B_theorie_f-3}
\end{frame}

\begin{frame}{Zero field depolarization mechanisms (theory)}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_0B_theorie_f-2}
\end{frame}

\begin{frame}{Zero field depolarization mechanisms (theory)}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_0B_theorie_f-1}
\end{frame}

\begin{frame}{Zero field depolarization mechanisms (theory)}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_0B_theorie_f}
\end{frame}

\begin{frame}{Experiment: $\vec B$ in arbitrary direction}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_T1_PL_1x1x1x1_f-5}
\end{frame}

\begin{frame}{Experiment: $\vec B$ in arbitrary direction}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_T1_PL_1x1x1x1_f-4}
\end{frame}

\begin{frame}{Experiment: $\vec B$ in arbitrary direction}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_T1_PL_1x1x1x1_f-3}
\end{frame}

\begin{frame}{Experiment: $\vec B$ in arbitrary direction}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_T1_PL_1x1x1x1_f-2}
\end{frame}

\begin{frame}{Experiment: $\vec B$ in arbitrary direction}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_T1_PL_1x1x1x1_f-1}
\end{frame}

\begin{frame}{Experiment: $\vec B$ in arbitrary direction}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_T1_PL_1x1x1x1_f}
\end{frame}

\begin{frame}{Experiment: $\vec B \parallel [100]$}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_T1_PL_100_f-6}
\end{frame}

\begin{frame}{Experiment: $\vec B \parallel [100]$}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_T1_PL_100_f-5}
\end{frame}

\begin{frame}{Experiment: $\vec B \parallel [100]$}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_T1_PL_100_f-4}
\end{frame}

\begin{frame}{Experiment: $\vec B \parallel [100]$}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_T1_PL_100_f-3}
\end{frame}

\begin{frame}{Experiment: $\vec B \parallel [100]$}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_T1_PL_100_f-2}
\end{frame}

\begin{frame}{Experiment: $\vec B \parallel [100]$}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_T1_PL_100_f-1}
\end{frame}

\begin{frame}{Experiment: $\vec B \parallel [100]$}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_T1_PL_100_f}
\end{frame}

\subsection{Conclusion}
\begin{frame}{Conclusion}
\begin{itemize}
\item The use of NV center ensemble for magnetometry is currently limited by the interactions between the spin defects.
\pause
\bigskip
\item Dipole-dipole interaction within dense ensemble of NV centers result in spin depolarization. This effect is stronger in zero-field.
\pause
\bigskip
\item This depolarization can be used to perform microwave-free and orientation-free magnetometry at low magnetic field.
\pause
\bigskip
\item The physics of low-field depolarization is complex and need to be further studied to improve the performances of LFDM.
\end{itemize}

@@

\begin{frame}{Acknowledgments}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Remerciements}
\end{frame}

@@

\begin{frame}{NV center magnetometry sensitivity}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_NV_limite_sensi}
\end{frame}

@@

\begin{frame}{Angular sensitivity of LFDM}
\centering
\includegraphics[width=\textwidth,height=0.85\textheight,keepaspectratio]{Slide_angular_sensitivity}
\end{frame}

\end{document}
